\documentclass[10pt]{article} 
%\usepackage{libertine}
%\usepackage[T1]{fontenc}
%\usepackage{nopageno}
%------------------------Dimensions--------------------------------------------
\topmargin=-0.5in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=-0.4in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=7in %How wide you want your text to be
\marginparwidth=0.5in
%\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=10.0in %How tall the text body is allowed to be on each page
\linespread{1.07}

\usepackage[linktocpage=true]{hyperref}
\hypersetup{colorlinks=true,citecolor=blue, linkcolor=blue, urlcolor=blue}

\renewcommand{\labelitemi}{$\diamond$}

\begin{document}
\LARGE\centerline{<-NAME->}
\normalsize \centerline{<-ADDRESS->}
\centerline{\texttt{07900473091}   \hspace{3mm} \texttt{sh0799@my.bristol.ac.uk}\hspace{3mm} samhatfield.co.uk}
\noindent
%\line(1,0){505}

\noindent\rule{505pt}{0.6pt}\\
\noindent {\Large Experience}\\
\noindent {\sc Computer Programmer, Microcosm} \hfill \textsc{August 2014 - present}
\begin{itemize}
\item Helped to develop SmartSign, a two-factor authentication system for web developers, working on all aspects of the front end and back end. 
\item Ported the API from PHP to ASP.NET.
\end{itemize}

\noindent{\sc Summer Intern, Surrey Space Centre, University of Surrey} \hfill \textsc{Summer 2013}
\begin{itemize}
		\item Designed and built a Cherenkov radiation detector. 
		\item Learnt how to prototype electronic circuits, using integrated circuits, oscilloscopes, signal generators etc.
		\item Provided valuable experience of working in a research environment, e.g. how to acquire materials, liaise with senior members of staff.
		\item Developed MATLAB scripts for processing data from geostationary satellites on high energy electrons in the radiation belts.
		\end{itemize}

\noindent {\sc Summer Intern, Earth Sciences Department, University of Bristol} \hfill \textsc{Summer 2012}
\begin{itemize}
		\item Studied exploration geophysics, specialising in gravity surveys.
		\item Analysed data from geophysical surveys of Lamb Leer cave, Somerset, using MATLAB.
		\item Gained hands-on experience with data collection in the field, as part of a team. 
\end{itemize}

\noindent\rule{505pt}{0.6pt}

\noindent {\Large Education}\\
\noindent {\sc MSci Physics, University of Bristol}  \hfill \textsc{2010-2014}
\begin{itemize}
              \item \emph{Grades}: Awarded first-class honours with an average mark of 78\%.
               \item \emph{Final year project}: ``Knots in geometrically-confined  polymers: nanochannels and other geometries''. Developed polymer model in {\tt C}. Involved extensive numerical modelling and use of the university Linux supercluster. 
		  \item \emph{Laboratory}: Extensive laboratory experience, including atomic resolution imaging of graphite through scanning tunnelling microscopy.
		  \item \emph{Group work}: Led group of 7 to write a 10,000 word review article on nuclear power.
%              \item \emph{Optional units}: Taken/taking courses on  the philosophy of physics, general relativity, relativistic field theory, condensed matter, stellar structure and evolution, quantum information theory, quantum chaos and more.
              \item \emph{Awards}: On the highly-commended list of applicants to the Undergraduate Awards in 2014, for my final year project. Received commendations for first year exam results and final year project, the first prize award in the final year poster session for external moderators and the Bristol PLuS Award for employability skills.
 \end{itemize}



\noindent {\sc Therfield School} \hfill 2003-2010
\begin{itemize}
	\item A Levels: Maths (A*), Physics (A*), Chemistry (A)
	\item Completed Open University 10cp short course: ``Planets: An Introduction''.
\end{itemize}

\noindent\rule{505pt}{0.6pt}\\
\noindent {\Large Other skills}
	
\begin{itemize}
		\item {\it Computing}: Experienced with Windows and Mac and familiar with Linux/UNIX. Confident with {\tt C}, MATLAB and Processing. Some experience with Python and BASH scripting, JavaScript,  CSS and  HTML. Regular user of the UNIX command line and also the \LaTeX~typesetting system. 
		\item {\it Electronics}: Enjoy building circuits and programming for Arduino and Raspberry Pi.
\end{itemize}

\noindent\rule{505pt}{0.6pt}\\
\noindent {\Large Interests \& responsibilities}
	\begin{itemize}
		\item Helped with developing a high altitude balloon, with a significant contribution to the launch logistics. Successfully launched in June 2014 to an altitude of 31.7 km. 
		%See \href{http://www.samhatfield.co.uk/projects/balloon}{samhatfield.co.uk/projects/balloon}.
		\item Member of Robogals, 2013-14, for promoting STEM subjects in schools. Volunteered for sessions to teach kids robotics.
		\item Secretary for student film club in Bristol, 2012-13, with administrative and organisational duties. 
		\item Keen reader of science, philosophy, economics, science fiction and American literature.
		\item Playing the piano, passed Grade 8 with distinction.
\end{itemize}



\end{document}
